\documentclass{letter}
\usepackage{lipsum}
\usepackage[shortlabels]{enumitem}
\signature{Mukund Balaji Srinivas \textit{mukundbalaji.srinivas@anu.edu.au} }
\usepackage[a4paper, total={6in, 8in}]{geometry}
\begin{document}
\begin{letter}{Subject: ANU Student caller Application }
\opening{Dear Sir/Madam}
I am a post graduate international student at the Australian National University studying computer science. I am looking for job opportunities that help leverage my existing skills while helping me develop further in areas where I feel there are good opportunities.\\ \\
 While looking for opportunities, I came across this position titled “ANU Student Caller”, which I feel is a great fit for my profile and leverages my skills with data (storing and maintaining data) and my language skills. This position leverages my ability to convey messages in a crisp but engaging manner (my IELTS overall score was 8.0) but helps me develop this skill further, given the opportunities to engage with alumni / seniors from diverse nationalities with varied backgrounds and communication styles. \\ \\
Further, I have a learner’s mindset and am enthused when there are opportunities to learn new skills (soft skills or IT applications / tools etc.)  or when I have an opportunity to engage with diverse cultures or on diverse topics, keeping in mind cultural and confidentiality related sensitivities. I generally approach my work in a structured and organized manner ensuring that the deliverables that I am tasked with are performed with utmost accuracy and attention to detail. Here are some examples in support of the above:
\begin{enumerate}[(a)]
	\item learnt a programming language called dart while working as a frontend developer for an IoT startup incubated in IIT-Madras, 
	\item analyzed satellite images to draw insights from them and report them without missing any of the technical details and,
	\item engaging with stakeholders – both external and internal, from diverse environments – to explain the outcomes, processes with all relevant details 
\end{enumerate}
 Moreover, residing at Toad Hall provides easy access to opportunities on campus, whereby I am available on the evenings (5:00 PM to 8:00 PM) on weekdays and all day on the weekends.
\\Finally, I am appreciative of the supportive environment that ANU offers for its students to grow and improve their skills. I appreciate this opportunity specifically as it provides me a good chance to learn, grow and build new connections (with my fellow students and staff outside of my direct contact list) and enhances my network within my alma meter! \\ \\
Thank you and hoping to hear from you soon.
\closing{Regards}
\end{letter}
\end{document}