\documentclass{resume_class}
\begin{document}
%%%
\pagestyle{resume}
%%%
%Work
\section{Work}
%%Latest IIT-M Dev expirence
\designation{Project Associate}{Indian Institute of Technology - Madras, India}{August to December 2021}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
	\item \mdseries  {Hands on approach to programming, solving critical problems that might otherwise lead to systematic inefficiencies.}
		\item \mdseries  {in-depth understanding of technical communication especially while facing the customer. }
	\item \mdseries  {Timely delivery of software updates that adhere to the customer’s requirements. }
	\item \mdseries  {Frequent and iterative Documentation of software, adhering to best practices. }
\end{itemize}

%%Amnex Experience
\designation{GIS Consultant}{Amnex Infotech - Ahmedabad, India}{July to December 2019}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
	\item \mdseries  {Solving all technical, non-technical problems encountered during image classification and report generation, by gathering accurate inputs from multiple sources. }
	\item \mdseries  {Having a good working relationship with all the teams involved in image classification and ground verification by continued communication, thus ensuring the report is accurate. Compile reports and supporting documents.}
	\item \mdseries  {Provide technical support to the ground data collection team by taking timely feedback and making UI changes.}
	\item \mdseries  {Frequent and iterative Documentation of software, adhering to best practices. }
\end{itemize}
%%%
%%Education
\section{Education}
%ANU 
\designation{Masters in Computing}{Australian National University, Canberra}{Feb 2021 - \textit{present}}
%BIT Mesra
\designation{Masters of Technology, Remote Sensing}{Birla Institute of Technology, Mesra}{June 2017 - June 2019}
%SASTRA Uni
\designation{Bachelors of Technology, Civil Engineering}{SASTRA University, Tanjore}{June 2012 - Nov 2016}
%%%
%%Skills
\section{Skills}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt , label =  {\small $\bullet$} ] 
	\item \mdseries \Large  {Experience supporting Learning Management Systems }
	\item \mdseries \Large {Learning content development }
	\item \mdseries \Large  {Technology support }
\end{itemize}

%%%
%%Hobbies, Languages
\section{Extra Curriculars }
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt , label =  {\small $\bullet$} ] 
	\item \mdseries \large  {Music \hspace {0.1 mm} $ \boldsymbol{|} $ }  \normalsize{Carnatic Classical Vocal} 
	\item \mdseries \large {Sports \hspace {0.15 mm}$ \boldsymbol{|} $ }  \normalsize {Badminton , Tennis}
	\item \mdseries \large  {Languages $ \boldsymbol{|} $ }  \normalsize{Telugu, Tamil, Hindi} 
\end{itemize}
\end{document}
