\documentclass{article}
\usepackage[shortlabels]{enumitem}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{sectsty}
\usepackage{hyperref}
\title{Why am I a good fit for the position}
\author{Mukund Balaji Srinivas\\\textit{mukundbalaji.srinivas@anu.edu.au}}

\begin{document}

\maketitle

\sectionfont{\small}
\subsectionfont{\small}

\subsection*{Motivation and Curiosity}
% Include GradResidence stuff for curiousity
\begin{itemize}
    \item {Co-founded \href{https://gradresidence.com/}{GradResidence}, a company dedicated to supporting international students by alleviating their cost of living pressures. The primary services include assisting students in securing part-time employment opportunities in the hospitality and retail sectors.}
    \item {Additionally, GradResidence plans to roll out iOS and \href{https://github.com/gradresidence/android}{Android}-based products to simplify the process of finding accommodation for international students, further enhancing their overall experience.} 
    
\end{itemize}

\subsection*{Collaboration and Communication Skills}
\begin{itemize}
    % Include PMI canberra chapter membership and the work you have been doing for them in building their website
    \item An active member of the PMI Canberra Chapter, contributing to website development projects and enhancing the online presence. Recently involved in migrating the website to better integrate with the Mailchimp marketing platform.
    % Include the Software Construction Project
    \item Participated in the Software Construction (COMP6442) \href{https://gitlab.cecs.anu.edu.au/u7544253/ga-23s1-comp2100-6442} {Project}, collaborating with a team to design, develop, and deploy a software application. The project aimed to incentivize going green by awarding points to users for proper recycling and making responsible decisions about the planet in their daily lives, demonstrating strong communication and teamwork skills.
    % Include RattleNG 
    \item Contributed to the development of \href{https://github.com/gjwgit/rattleng}{RattleNG}, a data mining platform originally written in C using the RGTK2 frameworks. The current efforts involve migrating to Flutter, a robust framework, working closely with team members to implement new features and improve the overall functionality of the application.
\end{itemize}

\subsection*{Java}
\begin{itemize}
    %Include The implementation of AVL Trees 
    \item \textbf{AVL Trees:} Developed an implementation to efficiently rank various users.
    %Include the Implementation of Hashing 
    \item \textbf{Hashing:} Created a hashing mechanism to efficiently compare two users based on various parameters.
    %Include the Implementation of Storing Data locally
    \item \textbf{Storing Data Locally:} Designed and implemented a system for storing frequently used user data locally.
\end{itemize}




\end{document}
