\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=1in}

\title{Service Level Agreement (SLA) for GradResidence}
\date{}
\begin{document}

\maketitle

\section*{1. Introduction}
This Service Level Agreement (SLA) is made between GradResidence ("Service Provider") and Vanessa A. Etika ("Client") for the provision of house hunting and share home arrangement services.

\section*{2. Scope of Services}
GradResidence will provide the following services to the Client:
\begin{itemize}
    \item Answering rental ads
    \item Inspecting potential homes
    \item Reporting based on the Client's preferences
\end{itemize}

\section*{3. Service Locations}
The services are available in the following locations:
\begin{itemize}
    \item Canberra
    \item Sydney
    \item Melbourne
\end{itemize}

\section*{4. Payment Terms}
\begin{itemize}
    \item The payment is after the first 4 reports have been submitted to the Client or the signing of the tenancy agreement, whichever is earlier.
    \item The fee covers the first 5 inspections of potential homes.
    \item Additional inspections and reports will incur a cost of \$15 AUD per property.
\end{itemize}

\section*{5. Notice Period}
The Client must provide at least 3 weeks' notice before their move-in date to utilize the services of GradResidence.

\section*{6. Service Performance}
GradResidence commits to the following performance standards:
\begin{itemize}
    \item Respond to client inquiries within 24 hours.
    \item Provide weekly updates on the progress of the house hunting process.
    \item Ensure that the share home arranged meets the Client's requirements as closely as possible.
\end{itemize}

\section*{7. Responsibilities}
\subsection*{GradResidence Responsibilities:}
\begin{itemize}
    \item Provide professional and timely services as described in this agreement.
    \item Communicate effectively with the Client regarding the progress of the house hunting process.
    \item Ensure all inspections and communications with landlords are conducted professionally.
    \item Generate an invoice after the first 4 reports have been generated.
\end{itemize}

\subsection*{Client Responsibilities:}
\begin{itemize}
    \item Provide accurate and complete information regarding their housing preferences and requirements.
    \item Pay the fee after 4 property reports are received.
    \item For more than 5 properties, the fee has to be paid after every report.
    \item Respond promptly to any communications from GradResidence.
\end{itemize}

\section*{8. Confidentiality}
Both parties agree to maintain the confidentiality of any proprietary or sensitive information exchanged during the course of this agreement.

\section*{9. Terms \& Conditions}
\begin{itemize}
    \item This SLA is valid until the Client wants to avail these services.
    \item GradResidence reserves the right to modify the terms of this SLA with prior written notice to the Client.
    \item In case of any disputes, both parties agree to seek resolution through mutual agreement or mediation.
\end{itemize}

\section*{10. Termination}
Either party may terminate this agreement with 24 hours' prior written notice. In the event of termination, the Client will be liable to pay for any services already rendered and the upfront fee will be non-refundable.

\section*{11. Contact Information}
For any questions or concerns related to this SLA or the services provided, please contact:
\begin{itemize}
    \item \textbf{Website}: \href{http://www.gradresidence.com}{GradResidence.com}
    \item \textbf{Phone}: 0405076587
    \item \textbf{Email}: \href{mailto:admin@gradresidence.com}{admin@gradresidence.com}
\end{itemize}

\vspace{1cm}

\section*{Acknowledgement and Agreement}
By signing below, both parties agree to the terms and conditions outlined in this SLA.

\vspace{1cm}

\noindent \textbf{Service Provider:} \\
GradResidence \\
\noindent \rule{10cm}{0.4pt} \\
Signature

\vspace{1cm}

\noindent \textbf{Client:} \\
Vanessa A. Etika \\
\noindent \rule{10cm}{0.4pt} \\
Signature

\vspace{1cm}

\noindent \textbf{Date:} \\
\noindent \rule{10cm}{0.4pt}

\end{document}
