\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=1in}

\title{Service Level Agreement (SLA) for GradResidence}
\date{}
\begin{document}

\maketitle

\section*{1. Introduction}
This Service Level Agreement (SLA) is made between GradResidence ("Service Provider") and [Client Name] ("Client") for the provision of house hunting and share home arrangement services.

\section*{2. Scope of Services}
GradResidence will provide the following services to the Client:
\begin{itemize}
    \item Answering rental ads
    \item Inspecting potential homes
    \item Finding and securing a suitable share home for the Client before their arrival in Australia
\end{itemize}

\section*{3. Service Locations}
The services are available in the following locations:
\begin{itemize}
    \item Canberra
    \item Sydney
    \item Melbourne
\end{itemize}

\section*{4. Payment Terms}
\begin{itemize}
    \item The Client agrees to pay an upfront fee of \$100 AUD before availing the services of GradResidence.
    \item This fee covers the first 5 inspections of potential homes.
    \item Any additional inspections beyond the first 5 will incur an additional cost based on the distance traveled for each inspection. The cost details will be provided to the Client in advance.
\end{itemize}

\section*{5. Notice Period}
The Client must provide at least 3 weeks' notice before their arrival date to utilize the services of GradResidence.

\section*{6. Service Performance}
GradResidence commits to the following performance standards:
\begin{itemize}
    \item Respond to client inquiries within 24 hours.
    \item Provide weekly updates on the progress of the house hunting process.
    \item Ensure that the share home arranged meets the Client's requirements as closely as possible.
\end{itemize}

\section*{7. Responsibilities}
\subsection*{GradResidence Responsibilities:}
\begin{itemize}
    \item Provide professional and timely services as described in this agreement.
    \item Communicate effectively with the Client regarding the progress of the house hunting process.
    \item Ensure all inspections and communications with landlords are conducted professionally.
\end{itemize}

\subsection*{Client Responsibilities:}
\begin{itemize}
    \item Provide accurate and complete information regarding their housing preferences and requirements.
    \item Respond promptly to any communications from GradResidence.
    \item Pay the agreed upfront fee of \$100 AUD before the service commencement.
    \item Cover any additional costs for inspections beyond the first 5 as agreed upon.
\end{itemize}

\section*{8. Confidentiality}
Both parties agree to maintain the confidentiality of any proprietary or sensitive information exchanged during the course of this agreement.

\section*{9. Terms \& Conditions}
\begin{itemize}
    \item This SLA is valid from the date of agreement and remains in effect until the services are delivered and the Client has settled into their new home.
    \item GradResidence reserves the right to modify the terms of this SLA with prior written notice to the Client.
    \item In case of any disputes, both parties agree to seek resolution through mutual agreement or mediation.
\end{itemize}

\section*{10. Termination}
Either party may terminate this agreement with 7 days' written notice. In the event of termination, the Client will be liable to pay for any services already rendered and the upfront fee will be non-refundable.

\section*{11. Contact Information}
For any questions or concerns related to this SLA or the services provided, please contact:
\begin{itemize}
    \item \textbf{Website}: \href{http://www.gradresidence.com}{GradResidence.com}
    \item \textbf{Phone}: 0405076587
    \item \textbf{Email}: \href{mailto:admin@gradresidence.com}{admin@gradresidence.com}
\end{itemize}

\vspace{1cm}

\section*{Acknowledgement and Agreement}
By signing below, both parties agree to the terms and conditions outlined in this SLA.

\vspace{1cm}

\noindent \textbf{Service Provider:} \\
GradResidence \\
\noindent \rule{10cm}{0.4pt} \\
Signature

\vspace{1cm}

\noindent \textbf{Client:} \\
 \\
\noindent \rule{10cm}{0.4pt} \\
Signature

\vspace{1cm}

\noindent \textbf{Date:} \\
\noindent \rule{10cm}{0.4pt}

\end{document}
