\documentclass{resume_class}
\pagecolor{White}
\usepackage{hyperref}
\begin{document}
%%%
\pagestyle{resume}
%%%
% Work Experience
\section{Work Experience}
%% GradResidence Experience
\designation{Co-founder}{GradResidence}{May 2024 - Present}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Supported international students by easing their cost of living pressures through securing part-time employment opportunities in the hospitality and retail sectors.}
    \item \mdseries {Planned and developed iOS and Android-based products to simplify the process of finding accommodation for international students.}
    \item \mdseries {Lead the development team and successfully launched the GradResidence mobile application for both iOS and Android platforms.}
\end{itemize}

%% PMI Canberra Experience
\designation{Website Developer}{PMI Canberra Chapter}{March 2024 - Present}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Contributed to website development projects and enhanced the online presence of the PMI Canberra Chapter.}
    \item \mdseries {Migrated the website to better integrate with the Mailchimp marketing platform, increasing efficiency and data accuracy.}
    \item \mdseries {Implemented new features and functionalities to enhance user engagement and experience.}
\end{itemize}

%% RattleNG Experience
\designation{Software Developer}{RattleNG Project}{November 2023 - Present}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Contributed to the development of RattleNG, a data mining platform originally written in C using the RGTK2 frameworks.}
    \item \mdseries {Migrated the platform to Flutter, working closely with team members to implement new features and improve the overall functionality of the application.}
    \item \mdseries {Led the development of the Android version of the RattleNG application, ensuring a seamless cross-platform experience.}
\end{itemize}

%% IIT-M Experience
\designation{Project Associate}{Indian Institute of Technology - Madras, India}{August 2021 - December 2021}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Entered sensor information for front-end tests in JSON.}
    \item \mdseries {Communicated with hardware and networking teams to include changes in the front-end.}
    \item \mdseries {Coordinated the data collection process, ensuring accurate and timely data gathering for the project.}
\end{itemize}

%% Amnex Experience
\designation{GIS Consultant}{Amnex Infotech - Ahmedabad, India}{July 2019 - December 2019}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Responded to queries by the technical and non-technical teams of the organization.}
    \item \mdseries {Maintained a good working relationship with all teams involved in image classification and ground verification by continuous communication, ensuring accurate reports. Compiled reports and supporting documents.}
    \item \mdseries {Created reports on short notice when requested by management.}
\end{itemize}

\newpage
%% Education
\section{Education}
\designation{Masters in Computing}{Australian National University, Canberra}{Feb 2021 - Present}
\designation{Masters of Technology, Remote Sensing}{Birla Institute of Technology, Mesra}{June 2017 - June 2019}
\designation{Bachelors of Technology, Civil Engineering}{SASTRA University, Tanjore}{June 2012 - Nov 2016}

%% Skills
\section{Skills}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt , label =  {\small $\bullet$} ] 
    \item \mdseries {Proficient in Android development with Java and Kotlin.}
    \item \mdseries {Experienced in Flutter development for cross-platform mobile applications.}
    \item \mdseries {Strong problem-solving and analytical skills.}
    \item \mdseries {Excellent written and oral communication skills.}
    \item \mdseries {Experience with version control systems (Git).}
    \item \mdseries {Familiar with Agile development methodologies.}
    \item \mdseries {Ability to design and develop robust, scalable, and high-quality mobile applications.}
    \item \mdseries {Experience with integrating third-party libraries and APIs.}
    \item \mdseries {Strong understanding of the full mobile development life cycle.}
    \item \mdseries {Proficient in GIS software (ArcGIS Suite) and database management.}
    \item \mdseries {Proven experience in teamwork and relationship-building.}
    \item \mdseries {Excellent attention to detail and multitasking abilities.}
    \item \mdseries {High appreciation and understanding of Health \& Safety standards.}
    \item \mdseries {Strong motivation, curiosity, and eagerness to learn and grow.}
\end{itemize}

\end{document}