\documentclass{article}
\usepackage[shortlabels]{enumitem}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{sectsty}
\usepackage{hyperref}
\title{Why am I a good fit for the position}
\author{Mukund Balaji Srinivas\\\textit{mukundbalaji.srinivas@anu.edu.au}}

\begin{document}

\maketitle

\sectionfont{\small}
\subsectionfont{\small}

\subsection*{Technical Skills and Experience}
\begin{itemize}
    \item \textbf{GIS Experience:} Proficient in producing high-quality map outputs using ESRI's ArcGIS suite (ArcPro and ArcMap), with 1+ year of experience as a GIS Consultant at Amnex Infotech.
    \item \textbf{Database Experience:} Strong experience working with databases, having contributed to data mining platforms (RattleNG) and entered sensor data in JSON format at the Indian Institute of Technology - Madras.
    \item \textbf{Multidisciplinary Projects:} Familiarity with multidisciplinary projects, having worked with various teams at Amnex Infotech and the Indian Institute of Technology - Madras.
    \item \textbf{Independent Work:} Demonstrated ability to work independently with minimal supervision, as seen in my role as a Co-founder of GradResidence.
\end{itemize}

\subsection*{Communication and Teamwork}
\begin{itemize}
    \item \textbf{Communication Skills:} Excellent written and verbal communication skills, honed through roles at GradResidence, PMI Canberra Chapter, and various team projects.
    \item \textbf{Teamwork and Relationship Building:} Proven teamwork and relationship-building skills, as demonstrated in my roles at GradResidence, PMI Canberra Chapter, and collaborative projects like RattleNG and the Software Construction project.
    \item \textbf{Attention to Detail and Multitasking:} Strong attention to detail and ability to multitask, showcased in my roles at GradResidence and the Indian Institute of Technology - Madras.
\end{itemize}

\subsection*{Additional Skills and Motivation}
\begin{itemize}
    \item \textbf{Health \& Safety Standards:} High appreciation and understanding of Health \& Safety standards, with a commitment to adhering to these standards in all work environments.
    \item \textbf{Motivation and Curiosity:} Strong motivation and curiosity, as seen in my initiative to co-found GradResidence and contribute to various projects.
    \item \textbf{Eagerness to Learn:} Eagerness to learn and grow, with a willingness to expand my skills in areas such as ArcGIS web app/widget development, ArcGIS automation, and FME experience if given the opportunity.
\end{itemize}

\end{document}