\documentclass{letter}
\usepackage[shortlabels]{enumitem}
\signature{Mukund Balaji Srinivas \textit{mukundbalaji.srinivas@anu.edu.au} }
\usepackage[a4paper, total={6in, 9in}]{geometry}
\usepackage{hyperref}
\begin{document}
\begin{letter}{Hiring Team\\Canva}
\opening{Dear Hiring Team,}

As a postgraduate international student at the Australian National University, studying for a Master's in Computing, there is an eagerness to find job opportunities that utilize existing skills while allowing for further development in areas with significant potential for growth.

The position of Android Engineer at Canva presents an excellent match for this profile. This role leverages strong problem-solving skills and offers the opportunity to apply expertise in mobile application development.

With a strong learner's mindset, there is enthusiasm for acquiring new skills, both soft and technical. Passionate about engaging with diverse cultures while maintaining confidentiality, the approach to work is structured and organized, ensuring accurate and detailed deliverables. Below are examples highlighting these attributes:

\begin{enumerate}[(a)]
    \item Co-founded \href{https://gradresidence.com/}{GradResidence}, a company aimed at supporting international students by easing their cost of living pressures. We assist students in securing part-time employment opportunities in the hospitality and retail sectors. Additionally, we plan to roll out iOS and \href{https://github.com/gradresidence/android}{Android}-based products to simplify the process of finding accommodation for international students, enhancing their overall experience.
    \item An active member of the PMI Canberra Chapter, contributing to website development projects and enhancing the online presence. Recently, I was involved in migrating the website to better integrate with the Mailchimp marketing platform.
    \item Participated in the Software Construction (COMP6442) \href{https://gitlab.cecs.anu.edu.au/u7544253/ga-23s1-comp2100-6442}{Project}, collaborating with a team to design, develop, and deploy a software application. This project aimed to incentivize going green by awarding points to users for proper recycling and making responsible decisions about the planet in their daily lives, showcasing my strong communication and teamwork skills.
    \item Contributed to the development of \href{https://github.com/gjwgit/rattleng}{RattleNG}, a data mining platform originally written in C using the RGTK2 frameworks. The current efforts involve migrating to Flutter, a robust framework, where I work closely with team members to implement new features and improve the overall functionality of the application.
\end{enumerate}

I am enthusiastic about the opportunity to contribute to Canva and am particularly excited about this role as it provides a good chance to learn, grow, and build new connections within the team and the wider organization.

\closing{Thank you, Regards,}
\end{letter}
\end{document}
