\documentclass{article}
\usepackage[shortlabels]{enumitem}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{sectsty}
\usepackage{hyperref}
\title{Why am I a good fit for the position}
\author{Mukund Balaji Srinivas\\\textit{mukundbalaji.srinivas@anu.edu.au}}

\begin{document}

\maketitle

\sectionfont{\small}
\subsectionfont{\small}

% \subsection*{Motivation and Curiosity}
% % Include GradResidence stuff for curiousity
% \begin{itemize}
%     \item {Co-founded \href{https://gradresidence.com/}{GradResidence}, a company dedicated to supporting international students by alleviating their cost of living pressures. The primary services include assisting students in securing part-time employment opportunities in the hospitality and retail sectors.}
%     \item {Additionally, GradResidence plans to roll out iOS and \href{https://github.com/gradresidence/android}{Android}-based products to simplify the process of finding accommodation for international students, further enhancing their overall experience.} 
%     \item Created LinkedIn videos documenting my learning journey in functional programming to deepen my understanding of the concepts while sharing knowledge with the community.
% \end{itemize}

\subsection*{Collaboration and Communication Skills}
\begin{itemize}
    % Include PMI canberra chapter membership and the work you have been doing for them in building their website
    \item An active member of the PMI Canberra Chapter, contributing to website development projects and enhancing the online presence. Recently involved in migrating the website to better integrate with the Mailchimp marketing platform.
    % Include the Software Construction Project
    \item Participated in the Software Construction (COMP6442) \href{https://gitlab.cecs.anu.edu.au/u7544253/ga-23s1-comp2100-6442} {Project}, collaborating with a team to design, develop, and deploy a software application. The project aimed to incentivize going green by awarding points to users for proper recycling and making responsible decisions about the planet in their daily lives, demonstrating strong communication and teamwork skills.
    % Include RattleNG 
    \item Contributed to the development of \href{https://github.com/gjwgit/rattleng}{RattleNG}, a data mining platform originally written in C using the RGTK2 frameworks. The current efforts involve migrating to Flutter, a robust framework, working closely with team members to implement new features and improve the overall functionality of the application.
    \item Created LinkedIn videos documenting my learning journey in functional programming to deepen my understanding of the concepts while sharing knowledge with the community.
\end{itemize}

\subsection*{GIS}
\begin{itemize}
    \item Worked as a GIS Consultant at Amnex Infotech, gaining practical experience with ArcGIS products and working on large-scale spatial data projects. Developed strong problem-solving skills through close collaboration with both technical and non-technical teams.
    \item Hands-on experience using ArcGIS Desktop and ArcGIS Online for data analysis, geoprocessing, and visualization tasks. Created comprehensive reports with maps to assist stakeholders in decision-making processes.
    \item Applied Python for data-related tasks, including data cleaning, manipulation, and analysis, contributing to effective data management in GIS projects. Familiar with libraries such as Pandas and NumPy.
\end{itemize}




\end{document}
