\documentclass{letter}
\usepackage[shortlabels]{enumitem}
\signature{Mukund Balaji Srinivas \textit{mukundbalaji.srinivas@anu.edu.au} }
\usepackage[a4paper, total={7in, 9in}]{geometry}
\usepackage{hyperref}
\begin{document}
\begin{letter}{Hiring Team\\Hays}
\opening{Dear Hiring Team,}

As a postgraduate international student at the Australian National University, studying for a Master's in Computing, I am eager to find opportunities that align with my skills while offering avenues for growth in key areas, including spatial data management and geospatial technology.

The position of GIS Database Engineer presents an excellent match for my background. It provides the opportunity to leverage my experience with GIS tools and spatial data management, along with my problem-solving abilities, to maintain and enhance geospatial systems.

With a passion for continuous learning, I actively seek opportunities to develop new technical and soft skills. I thrive in collaborative environments, working effectively with diverse teams while ensuring organized and detail-oriented deliverables. Below are examples demonstrating these attributes:
\begin{enumerate}[(a)]
    
    \item While working with Amnex Infotech, I managed large-scale spatial data projects utilizing ArcGIS products, including ArcGIS Desktop and ArcGIS Online. I collaborated with both technical and non-technical teams to address challenges and ensure the delivery of precise geospatial reports.
    \item Utilized Python for document analysis tasks, including data cleaning, manipulation, and extraction. Familiar with libraries such as Pandas and NumPy, leveraging them to streamline workflows and enhance data management efficiency.
    \item Co-founded \href{https://gradresidence.com/}{GradResidence}, a company aimed at supporting international students by easing their cost of living pressures. We assist students in securing part-time employment opportunities in the hospitality and retail sectors. Additionally, we plan to roll out iOS and \href{https://github.com/gradresidence/android}{Android}-based products to simplify the process of finding accommodation for international students, enhancing their overall experience.
    \item An active member of the PMI Canberra Chapter, contributing to website development projects and enhancing the online presence. Recently, I was involved in migrating the website to better integrate with the Mailchimp marketing platform.
    \item Participated in the Software Construction (COMP6442) \href{https://gitlab.cecs.anu.edu.au/u7544253/ga-23s1-comp2100-6442}{Project}, collaborating with a team to design, develop, and deploy a software application. This project aimed to incentivize going green by awarding points to users for proper recycling and making responsible decisions about the planet in their daily lives, showcasing my strong communication and teamwork skills.
    \item Contributed to the development of \href{https://github.com/gjwgit/rattleng}{RattleNG}, a data mining platform originally written in C using the RGTK2 frameworks. The current efforts involve migrating to Flutter, a robust framework, where I work closely with team members to implement new features and improve the overall functionality of the application.
\end{enumerate}

I am enthusiastic about the opportunity to contribute to your organization and am particularly excited about this role, as it offers a valuable chance to enhance my expertise in GIS technologies, grow professionally, and collaborate with a dynamic team to drive impactful results within the public sector.

\closing{Thank you, Regards,}
\end{letter}
\end{document}
