\documentclass{resume_class}
\pagecolor{White}
\usepackage{hyperref}
\begin{document}
%%%
\pagestyle{resume}
%%%
% Work Experience
\section{Work Experience}

%% Amnex Experience
\designation{GIS Consultant}{Amnex Infotech - Ahmedabad, India}{July 2019 - December 2019}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Responded to queries by the technical and non-technical teams of the organization.}
    \item \mdseries {Maintained a good working relationship with all teams involved in image classification and ground verification by continued communication, ensuring accurate reports. Compiled reports and supporting documents.}
    \item \mdseries {Created reports on short notice when requested by management.}
\end{itemize}

%% IIT-M Experience
\designation{Project Associate}{Indian Institute of Technology - Madras, India}{August 2021 - December 2021}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Entered sensor information for front-end tests in JSON.}
    \item \mdseries {Communicated with hardware and networking teams to include changes in the front-end.}
\end{itemize}

%% Okami Experience
\designation{Kitchen Hand}{Okami Restaurant - Canberra, Australia}{March 2022 - June 2022}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Assisted chefs in food preparation and maintained kitchen cleanliness in a fast-paced environment.}
    \item \mdseries {Followed food safety standards and ensured smooth kitchen operations during peak hours.}
\end{itemize}

%% Canberra Labour Hire Experience
\designation{Construction Worker}{Canberra Labour Hire - Canberra, Australia}{June 2022 - September 2022}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Performed general labour duties at various construction sites, supporting tradespeople and site supervisors.}
    \item \mdseries {Maintained workplace safety standards and contributed to timely completion of tasks.}
\end{itemize}

%% McDonalds Experience
\designation{Crew Member}{McDonald's - Canberra, Australia}{October 2022 - March 2024}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Provided customer service, handled transactions, and prepared food orders efficiently.}
    \item \mdseries {Worked as part of a team to maintain high standards of service, cleanliness, and food quality.}
\end{itemize}

%% RattleNG Experience
\designation{Software Developer}{RattleNG Project}{November 2023 - December 2024}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Contributed to the development of \href{https://github.com/gjwgit/rattleng}{RattleNG}, a data mining platform originally written in C using the RGTK2 frameworks.}
    \item \mdseries {Migrated the platform to Flutter, working closely with team members to implement new features and improve the overall functionality of the application.}
\end{itemize}

%% PMI Canberra Experience
\designation{Website Developer}{PMI Canberra Chapter}{March 2024 - December 2024}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Contributed to website development projects and enhanced the online presence of the PMI Canberra Chapter.}
    \item \mdseries {Migrated the website to better integrate with the Mailchimp marketing platform.}
\end{itemize}

%% Coles Experience
\designation{Customer Service Team Member}{Coles Group}{April 2024 - Present}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Delivered high-quality customer service by assisting shoppers, resolving queries, and ensuring a positive store experience.}
    \item \mdseries {Operated checkout systems efficiently while maintaining accuracy in transactions and cash handling.}
    \item \mdseries {Collaborated with team members to maintain store presentation, stock shelves, and meet daily operational goals.}
\end{itemize}

%% GradResidence Experience
\designation{Co-founder}{GradResidence}{May 2024 - December 2024}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Supported international students by easing their cost of living pressures through securing part-time employment opportunities in the hospitality and retail sectors.}
    \item \mdseries {Planned and developed iOS and \href{https://github.com/gradresidence/android}{Android}-based products to simplify the process of finding accommodation for international students.}
\end{itemize}


\newpage
%% Education
\section{Education}
\designation{Masters in Computing}{Australian National University, Canberra}{Feb 2021 - Present}
\designation{Masters of Technology, Remote Sensing}{Birla Institute of Technology, Mesra}{June 2017 - June 2019}
\designation{Bachelors of Technology, Civil Engineering}{SASTRA University, Tanjore}{June 2012 - Nov 2016}

%% Skills
\section{Skills}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt , label =  {\small $\bullet$} ] 
    \item \mdseries {Proficient in Android development with Java and Kotlin.}
    \item \mdseries {Experienced in Flutter development for cross-platform mobile applications.}
    \item \mdseries {Strong problem-solving and analytical skills.}
    \item \mdseries {Excellent written and oral communication skills.}
    \item \mdseries {Experience with version control systems (Git).}
    \item \mdseries {Familiar with Agile development methodologies.}
    \item \mdseries {Ability to design and develop robust, scalable, and high-quality mobile applications.}
    \item \mdseries {Experience with integrating third-party libraries and APIs.}
    \item \mdseries {Strong understanding of the full mobile development life cycle.}
\end{itemize}

\end{document}
