\documentclass{resume_class}
\pagecolor{White}
\begin{document}
	%%%
	\pagestyle{resume}
        \section{Work}
        %%Latest retail  expirence
\designation{Retail Associate}{M.S.Y Technologies - Canberra}{January - 2023 to March - 2023}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
	\item \mdseries  {Provide excellent customer service to enhance customer satisfaction and loyalty.}
	\item \mdseries  {Ensure accurate and timely maintenance of POS systems to support sales and operations.}
        \item \mdseries  {Troubleshoot and resolve technical issues related to products and systems, such as motherboards, to ensure smooth operations and customer satisfaction.}
          
\end{itemize}
%%IIT-M Dev expirence
\designation{Project Associate}{Indian Institute of Technology - Madras, India}{August to December 2021}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
\item \mdseries  {Communicated effectively with clients to address technical issues and track feature requests.}
	\item \mdseries  {Maintained accurate and up-to-date records of client interactions and technical progress.}
        \item \mdseries  {Collaborated with team members to delegate tasks and ensure timely completion of projects.}
                  \item \mdseries  {Demonstrated strong problem-solving skills to effectively resolve technical issues and provide excellent customer service.}
          
          
\end{itemize}

%%Amnex Experience
\designation{GIS Consultant}{Amnex Infotech - Ahmedabad, India}{July to December 2019}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
\item \mdseries{Generate crop-wise acerage,damage and yeild estimates}
        \item \mdseries{Implement scalable classification models on optical satellite imagery.}
        \item \mdseries{Produce procedural documentation, leading to effective knowledge sharing amongst between technical and non-technical teams}
          \item \mdseries{Develop and deploy web mapping services using ArcGIS server}
          
	
	
\end{itemize}
%%%
%%Education
\section{Education}
%ANU 
\designation{Masters in Computing}{Australian National University, Canberra}{Feb 2021 - \textit{present}}
%BIT Mesra
\designation{Masters of Technology, Remote Sensing}{Birla Institute of Technology, Mesra}{June 2017 - June 2019}
%SASTRA Uni
\designation{Bachelors of Technology, Civil Engineering}{SASTRA University, Tanjore}{June 2012 - Nov 2016}
%%%
%%Projects

%%%
%%%References
% \section{Referees}              
% \begin{tabular}{c|c|c} 
% \textbf{Ninad Bhat} & \textbf{Dr Babji Srinivasan} & \textbf{Ashish Agarwal} \\
% Software Engineer & Associate Professor & Senior Research management Officer \\
% Software Innovation Institute  & Department of Applied Mechanics & Australian National University \\
% Australian National University & Indian Institute of Technology, Madras & ashish.agarwal@anu.edu.au  \\
% ninad.bhat@anu.edu.au & babji.srinivasan@iitm.ac.in  \\
		
    %   \end{tabular}

%%%
%%Skills
\section{Skills and Availability}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
                     \item \mdseries{Communication}
                     \item \mdseries{Time Management}
                     \item \mdseries{Microsoft Office}
                     \item \mdseries{Operating POS Machine: Square}
                     \item \mdseries{Service Delivery Management tools : Jira}
                     \item \mdseries{Languages : English, Hindi, Telugu, Tamil, Bengali}
                                            \item \mdseries{Availability: Monday,Tuesday,Friday,Saturday,Sunday (All day)}
                       

\end{itemize}           
                       
                     
             
\end{document}
