\documentclass{letter}
\usepackage{lipsum}
\usepackage[shortlabels]{enumitem}
\signature{Mukund Balaji Srinivas \\ \textbf{0405076587} \textit{mukundsrinivasb@hotmail.com}  }
\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=25mm,
 top= -40mm,
 }
\begin{document}
\begin{letter}{\textbf{Subject:} Applicantion for Retail Advisor Position at Howards Storage World }
\opening{Dear Sir/Madam}
I am writing to express my strong interest in the Retail Advisor position at Howards Storage World. As a Computer Science student with a keen interest in retail and a track record of successfully multitasking, I believe that my skills and dedication make me a well-suited candidate for this role.

While my retail experience is currently limited to a 3-month position as a sales associate at MSY Technologies, I have quickly developed a strong understanding of customer service and sales techniques. During this time, I successfully assisted customers in finding the right products, communicated product features effectively, and contributed to meeting sales targets.

As a Computer Science student, I have demonstrated my ability to manage multiple responsibilities effectively. Balancing academic coursework with part-time work has allowed me to develop excellent time management skills, adaptability, and a strong work ethic.

I am enthusiastic about the opportunity to provide organization solutions to customers at Howards Storage World, contribute to meeting sales targets, and actively pursue promotional opportunities. I am confident that my dedication, adaptability, and willingness to learn make me a valuable asset to the team.

Thank you for considering my application. I would appreciate the opportunity to discuss how my skills and enthusiasm align with the Retail Advisor position at Howards Storage World.
\closing{Regards,}
\end{letter}
\end{document}