\documentclass{resume_class}
\pagecolor{White}
\begin{document}
%%
\pagestyle{resume}
\section{Work}


%%Coles Experience
%% Coles Experience
\designation{Team Member - Customer Service}{Coles - Manuka, Canberra}{April 2024 - Present}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Delivered exceptional customer service by assisting customers with product inquiries, providing advice, and ensuring a positive shopping experience.}
    \item \mdseries {Efficiently operated checkout systems, processing transactions, handling cash, and balancing registers to maintain accuracy.}
    \item \mdseries {Collaborated with team members to restock shelves, maintain store cleanliness, and organize displays, contributing to a high-performance culture.}
    \item \mdseries {Demonstrated enthusiasm and passion for retail, adapting to a fast-paced environment and meeting daily operational goals.}
\end{itemize}



%% McDonalds Experience
\designation{Crew Member}{McDonalds - Manuka, Canberra}{August 2023 - March 2024}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt]
    \item \mdseries {Provided enthusiastic, customer-focused service in both storefront and drive-thru, ensuring a positive experience and high customer satisfaction.}
    \item \mdseries {Worked in a fast-paced, high-performance environment, collaborating with team members on food preparation, stock handling, and efficient back-of-house operations.}
\end{itemize}




%% Last Retail Experience
\designation{Retail Associate}{M.S.Y Technologies - Canberra}{January 2023 - March 2023}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
    \item \mdseries {Delivered enthusiastic and customer-focused service, assisting customers with product inquiries and ensuring a positive shopping experience.}
    \item \mdseries {Maintained accurate and timely operation of POS systems, supporting sales and overall store efficiency in a fast-paced environment.}
    \item \mdseries {Troubleshot and resolved technical issues for products and systems, contributing to smooth operations and customer satisfaction.}
    \item \mdseries {Collaborated effectively with team members to support merchandising, stock replenishment, and organized product displays.}
    \item \mdseries {Adapted to a high-performance, fast-paced retail environment while maintaining professionalism and attention to detail.}
\end{itemize}
%%%
%%Education
\section{Education}
%ANU 
\designation{Masters in Computing}{Australian National University, Canberra}{Feb 2021 - \textit{present}}
%BIT Mesra
\designation{Masters of Technology, Remote Sensing}{Birla Institute of Technology, Mesra}{June 2017 - June 2019}
%SASTRA Uni
\designation{Bachelors of Technology, Civil Engineering}{SASTRA University, Tanjore}{June 2012 - Nov 2016}
%%%
%%Projects

%%%
%%%References
% \section{Referees}              
% \begin{tabular}{c|c|c} 
% \textbf{Ninad Bhat} & \textbf{Dr Babji Srinivasan} & \textbf{Ashish Agarwal} \\
% Software Engineer & Associate Professor & Senior Research management Officer \\
% Software Innovation Institute  & Department of Applied Mechanics & Australian National University \\
% Australian National University & Indian Institute of Technology, Madras & ashish.agarwal@anu.edu.au  \\
% ninad.bhat@anu.edu.au & babji.srinivasan@iitm.ac.in  \\
		
    %   \end{tabular}

%%%
%%Skills
\section{Skills and Availability}
\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 2pt] 
                     \item \mdseries{Communication}
                     \item \mdseries{Time Management}
                     \item \mdseries{Microsoft Office}
                     \item \mdseries{Operating POS Machine: Square}
                     \item \mdseries{Service Delivery Management tools : Jira}
                     \item \mdseries{Languages : English, Hindi, Telugu, Tamil, Bengali}
                                            \item \mdseries{Availability: Monday,Tuesday,Friday,Saturday,Sunday (All day)}
                       

\end{itemize}           
                       
                     
             
\end{document}
