\documentclass{resume_class_casual}
\pagecolor{White}
\begin{document}
	%%%
	\pagestyle{resume}
	%%%
	%Work
	\section{Work}
	%%Latest Novotel Experience
	\designation{Room Assistant}{Novotel - Canberra}{May 2022 - \textit{present}}
	\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 1pt] 
		\item \mdseries  {Delivering hotel amenities.}
		\item \mdseries  {Greeting Guests.}
		\item \mdseries  {Maintenance of hotel property.}
	\end{itemize}
	
	%%Latest Okami Experience
	%%\designation{Kitchen Staff}{Okami - All You Can Eat , Braddon}{February - May 2022}
	%%\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 1pt] 
	%%%%	\item \mdseries  {Setup and Maintenance of dishwasher}
	%%	\item \mdseries  {Cleaning Dishes}
	
	%%\end{itemize}
	%%Hamleys Experience
	\designation{Crew Member}{Hamleys - Bengaluru, India}{December 2020 to October 2021}
	\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 1pt] 
		\item \mdseries  {Delivered excellent customer service by assisting customer purchases and grievances. }
		\item \mdseries  {Managed Sales counter and inventory re-stocking. }
		\item \mdseries  {Assisted logistics team for inter-store and inter-department movement and stock-take.}
	\end{itemize}
	
	%%Lifestyle Experience
	\designation{Sales Assistant}{Lifestyle - Bengaluru, India}{August 2019 to December 2020}
	\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 1pt] 
		\item \mdseries  {Greeted customer with product details and in-store promotions.}
		\item \mdseries  {Consistently delivered with High UPT and ATV.}
		\item \mdseries {Helped re-stock the store, stock-take, on call orders, etc. }
		
	\end{itemize}
	%%%
	%%Education
	\section{Education}
	%ANU 
	\designation{Masters in Computing}{Australian National University, Canberra}{Feb 2021 - \textit{present}}
	\designation{Bachelors of Technlogy - Civil Engineering}{SASTRA University, India}{}
	%%%
	%%Skills
	\section{Skills/Availability/Work Rights}
	\begin{itemize}[leftmargin = 10pt , labelsep = 3pt , parsep = 0pt , itemsep = 1pt , label =  {\small $\bullet$} ] 
		\item \mdseries \Large { \textbf{Language skills} : English - Fluent (IELTS 8.0) $|$ Hindi - native $|$ Tamil - native $|$ Telugu - Fluent $|$ Bengali - Fluent   }
		\item \mdseries \Large  {\textbf{Sales software} : POS such as Lightspeed, Bindo POS $|$ Salesforce $|$ Excel, Word, Powerpoint. }
		\item \mdseries \Large {\textbf{Availability} : Monday to Sunday $|$ 6 AM - 11 PM}
		\item \mdseries \Large {\textbf{Work Rights} : Student Visa (Subclass 500)  $|$ Up to 80 Hours \textit{per} fortnight}
		
	\end{itemize}
	
	%%% Work Rights
	\section{References}
	\begin{tabular}{|c|c|c|} 
		\textbf{Ashish Agarwal}  & \textbf{Vishal Kalaiperumal Suresh} & \textbf{Ram Kumar} \\
		Team Member & Australian Public Service & Team Member \\  
		David Jones & +61 432 250 342 & Just Jeans\\
		agg.caashish@gmail.com & & +61 452 606 540
	\end{tabular}	
\end{document}
