\documentclass{letter}
\usepackage{lipsum}
\usepackage[shortlabels]{enumitem}
\signature{Mukund Balaji Srinivas \textit{mukundbalaji.srinivas@anu.edu.au} }
\usepackage[a4paper, total={6in, 8in}]{geometry}
\begin{document}
\begin{letter}{Subject: IT Service Desk Officer Application }
\opening{Respected Ms Jacinda Euler Welsh}
I am a postgraduate international student at the Australian National University studying computer science. I am looking for job opportunities that help leverage my existing skills while helping me develop further in areas where I feel there are good opportunities.\\ \\
While looking for opportunities, I came across this position titled “IT Service Desk Officer”, which I feel is a great fit for my profile and leverages my problem solving skills. Further, this position leverages my ITIL certification in a real world environment. \\ \\
Further, I have a learner’s mindset and am enthused when there are opportunities to learn new skills (soft skills or IT applications / tools etc.)  or when I have an opportunity to engage with diverse cultures or on diverse topics, keeping in mind cultural and confidentiality related sensitivities. I generally approach my work in a structured and organized manner ensuring that the deliverables that I am tasked with are performed with utmost accuracy and attention to detail. Here are some examples in support of the above:
\begin{enumerate}[(a)]
	\item learnt a programming language called dart while working as a frontend developer for an IoT startup incubated in IIT-Madras, 
	\item analyzed satellite images to draw insights from them and report them without missing any of the technical details and,
	\item engaging with stakeholders – both external and internal, from diverse environments – to explain the outcomes, processes with all relevant details 
\end{enumerate}
 Moreover, as it is the semester break , I am available all day during weekdays and weekends.
\\Finally, I am appreciative of the supportive environment that BGGS offers its staff to grow and improve their skills. I appreciate this opportunity specifically as it provides me a good chance to learn, grow and build new connections (with staff outside of my direct contact list) and enhance my network.

\closing{Thank you, Regards}
\end{letter}
\end{document}